A comprehensive Ancestral Recombination Graph for SARS-CoV-2 inferred in real time

### 2025-09-24 latex/main.tex
Update title and fill out remaining metadata

\title{Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time}
\date{}

@@

\author[1]{Shing~H.~Zhan}
% TODO add joint second here?
\author[2,3]{Anastasia~Ignatieva}
\author[1]{Yan~Wong}
\author[4]{Katherine~Eaton}
\author[1]{Isobel~Guthrie}
\author[1]{Benjamin~Jeffery}
\author[1]{Duncan~S.~Palmer}
\author[4]{Carmen~Lia~Murall}
\author[5]{Sarah~P.~Otto}
\author[1\orcidlink{0000-0002-7894-5253}]{Jerome~Kelleher}

@@

\affil[1]{Big Data Institute, Li Ka Shing Centre for Health
Information and Discovery, University of Oxford, United Kingdom}
\affil[2]{Department of Statistics, University of Oxford, United Kingdom}
\affil[3]{School of Mathematics and Statistics, University of Glasgow, United Kingdom}
\affil[4]{National Microbiology Laboratory, Public Health Agency of Canada, Canada}
\affil[5]{Department of Zoology and Biodiversity Research Centre, University of British Columbia, Canada}

@@

% \affil[4]{Senior author}
% \affil[5]{Lead contact}

@@

%% TODO add correspodning - Shing and Jerome?
\affil[*]{Correspondence: first.last.jr@university.edu}
\affil[**]{Correspondence: f.middle.last@university.edu}

>>>>

\title{A comprehensive Ancestral Recombination Graph for SARS-CoV-2 inferred in real time}
\date{}

@@

\author[1,6]{Shing~H.~Zhan}
% TODO add joint second here?
\author[1,5]{Yan~Wong}
\author[2,5]{Anastasia~Ignatieva}
\author[3]{Katherine~Eaton}
\author[1]{Isobel~Guthrie}
\author[1]{Benjamin~Jeffery}
\author[1]{Duncan~S.~Palmer}
\author[3]{Carmen~Lia~Murall}
\author[4]{Sarah~P.~Otto}
\author[1\orcidlink{0000-0002-7894-5253}]{Jerome~Kelleher}

@@

\affil[1]{Big Data Institute, Li Ka Shing Centre for Health
Information and Discovery, University of Oxford, United Kingdom}
\affil[2]{Department of Statistics, University of Oxford, United Kingdom}
\affil[3]{National Microbiology Laboratory, Public Health Agency of Canada, Canada}
\affil[4]{Department of Zoology and Biodiversity Research Centre, University of British Columbia, Canada}

@@

\affil[5]{Joint second author}
\affil[6]{Lead contact}

@@

\affil[*]{Correspondence: shing.zhan@bdi.ox.ac.uk}
\affil[**]{Correspondence: jerome.kelleher@bdi.ox.ac.uk}
